\begin{thebibliography}{30}



\bibitem{lorentztransformations}
The {Lorentz} transformation - {University} of {Oxford} {Department} of {Physics} 
$<https://users.physics.ox.ac.uk/~smithb/website/coursenotes>$

\bibitem{rindlercoordinates}
Rindler, Wolfgang.  (1969).  Essential relativity; special, general, and cosmological.  New York :  Van Nostrand Reinhold Co

\bibitem{carollspacetime}
Spacetime and geometry
pg. 412 -   421

\bibitem{simplifiedderivation}
Simplified derivation of the Hawking-Unruh temperature for an
accelerated observer in vacuum

\bibitem{bhspacetime}
\textit{Pictures about space} -  Accessed 30 Nov 2016
$<http://pics-about-space.com/black-hole-sketch?p=1\#>$

\bibitem{surfacegravity}
Bardeen, J. M., Carter, B., Hawking, S. W. : Commun. math. Phys. 31, 161--170 (1973)

\bibitem{hawkradpic}
\textit{The physics of the universe} -  Accessed 30 Nov 2016
$http://www.physicsoftheuniverse.com/topics_blackholes_theory.html$

\bibitem{hartlegrav}
\textit{Gravity - An introduction to Einstein`s General Relativity - James B. Hartle} -  pages 292 - 294

\bibitem{schutz}
A first course in gravity Schutz
pages 323-327

\bibitem{massuniverse}
Paul Davies (2006). The Goldilocks Enigma. First Mariner Books. p. 43

\bibitem{asteroid}
http://nssdc.gsfc.nasa.gov/planetary/factsheet/asteroidfact.html

\bibitem{massuniverse3}
http://curious.astro.cornell.edu/about-us/101-the-universe/cosmology-and-the-big-bang/general-questions/579-what-is-the-mass-of-the-universe-intermediate

\end{thebibliography}